Adaptive timing of investment strategy

### 2022-04-14 notebook/cran_vignettes/SI8.Rmd
Initialise a new vignette to explain the simulated annealing approach

In the context of adaptive management of conservation conflict, managers tend to invest their ressources in updating the conservation policy as soon as possible. But leaving the policy unchanged when the population is close enough to the target could actually save money, time, and energy, and enpower managers for the next iteration.

>>>>

In the context of adaptive management of conservation conflict, managers tend to invest their resources in updating the conservation policy as soon as possible. But leaving the policy unchanged when the population is close enough to the target could actually save money, time, and energy, and enpower managers for the next iteration.
